<<<<<<< HEAD
<<<<<<< HEAD
---
title: "Activity"
author: "Baohua Wu"
date: "06/10/2014"
output: html_document
---

# Reproducible Research: Peer Assessment 1

## Loading and preprocessing the data

```{r,echo=TRUE}
act<-read.csv("activity.csv", header=TRUE)
str(act)
act$Date<-as.Date(act$date, format = "%Y-%m-%d")
head(act)
```

## What is mean total number of steps taken per day?
```{r,echo=TRUE}
tot_steps<-tapply(act$steps, act$Date, sum, na.rm=TRUE)
hist(tot_steps, xlab="Total Number of Steps Taken per Day", main="Histogram for Total Number of Steps per Day")
mean<-mean(tot_steps, na.rm=TRUE)
mean
median<-median(tot_steps, na.rm=TRUE)
median
```

## What is the average daily activity pattern?
```{r}
avg<-tapply(act$steps, act$interval, mean, na.rm=TRUE)
interval<-as.numeric(names(avg))

step<-as.data.frame(cbind(avg, interval))

require(ggplot2)
ggplot(step, aes(interval, avg)) + geom_line() +  xlab("Interval") + ylab("Avg Steps")

```


## Imputing missing values
```{r}
sum(is.na(act$steps)) 
wbh<-act[,-1]
wbh$steps<-ifelse(is.na(act$steps),mean(act$steps, na.rm=TRUE), act$steps)
#str(wbh)
#head(wbh)

tot_steps1<-tapply(wbh$steps, wbh$Date, sum, na.rm=TRUE)
hist(tot_steps1, xlab="Total Number of Steps Taken per Day", main="Histogram for Total Number of Steps per Day")
```

## What is the mean and median after imputing of missing?

```{r}
mean1<-mean(tot_steps1, na.rm=TRUE)
mean1
median1<-median(tot_steps1, na.rm=TRUE)
median1
```

## Are there differences in activity patterns between weekdays and weekends?

```{r}
wbh$day<-weekdays(wbh$Date)
wbh$wkd<-ifelse(wbh$day %in% c("Saturday", "Sunday"), "Weekend", "Weekday")

avg<-tapply(wbh[wbh$wkd=="Weekday",]$steps, wbh[wbh$wkd=="Weekday",]$interval, mean, na.rm=TRUE)
interval<-names(avg)
wkd<-"Weekday"
week<-as.data.frame(cbind(avg,interval,wkd))

avg<-tapply(wbh[wbh$wkd=="Weekend",]$steps, wbh[wbh$wkd=="Weekend",]$interval, mean, na.rm=TRUE)
interval<-names(avg)
wkd<-"Weekend"
week1<-as.data.frame(cbind(avg,interval,wkd))
wk<-rbind(week,week1)
require(lattice)
xyplot(as.numeric(levels(wk$avg))[wk$avg]~as.numeric(levels(wk$interval))[wk$interval] |wk$wkd, wk,layout = c(1, 2), xlab="Interval", ylab="Number of Steps",
  panel=function(x, y){
  panel.xyplot(x, y, lty=1, type="l")
}, as.table=T)
```

=======
=======
>>>>>>> dc20c7c4e92aea6af318a611e2669d5b9c6cbfaf
# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data



## What is mean total number of steps taken per day?



## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
<<<<<<< HEAD
>>>>>>> dc20c7c4e92aea6af318a611e2669d5b9c6cbfaf
=======
>>>>>>> dc20c7c4e92aea6af318a611e2669d5b9c6cbfaf
