---
title: "Impacts of Storms on Public Health and Economy in USA"
author: "Baohua Wu"
date: "06/10/2014"
output: html_document
---

# Synopsis

This report mainly studied how storms impacted both public health and economic problems for communities and municipalities.
The study found, Tornado, Excessive Heat, TSTM WIND are  the most harmful with respect to population health, Tornado , FlASH FLOOD, TSTM WIND etc.  have the greatest economic consequences. This study results may help to prioritize resources for different types of events in preparing for severe weather events.


## Data Processing
After reading in the origin data, a new data set called "storm" was subset to keep only those usufull variables for later analysis.

```{r, echo=TRUE, cache=TRUE}
wbh<-read.csv(bzfile("repdata-data-StormData.csv.bz2"))
storm<-wbh[,c("EVTYPE", 'FATALITIES', 'INJURIES',  'PROPDMG', 'CROPDMG')]
str(storm)
head(storm) 
#table(storm$EVTYPE)
```


### Get total number of fatalities/injuries by each type of storm event, and make the barcharts for comparisions:

```{r,echo=TRUE}
require(lattice)
fata<-tapply(storm$FATALITIES, storm$EVTYPE,sum, na.rm=TRUE)
Data<-fata[order(-fata)][1:10]
barchart(Data, xlab="Total Number", main="Total Number of Fatalities")

injury<-tapply(storm$INJURIES, storm$EVTYPE,sum, na.rm=TRUE)
Data<-injury[order(-injury)][1:10]
barchart(Data, xlab="Total Number", main="Total Number of Injuries")
```

### Get top ten damages by each type of storm event for properties damages:

```{r,echo=TRUE}
prop<-tapply(storm$PROPDMG, storm$EVTYPE,sum, na.rm=TRUE)
Num1<-prop[order(-prop)][1:10]
Num1
```

### Get top ten damages by each type of storm event for crop damages:

```{r,echo=TRUE}
crop<-tapply(storm$CROPDMG, storm$EVTYPE,sum, na.rm=TRUE)
Num2<-crop[order(-crop)][1:10]
Num2
```

### Get total damages by each type of storm event, and make the barchart for comparisions
```{r,echo=TRUE}
tot<-tapply(storm$PROPDMG+storm$CROPDMG, storm$EVTYPE,sum, na.rm=TRUE)
Tot=tot[order(-tot)][1:10]

barchart(Tot, xlab="Total Damages(Properties + Crops)", main="Total Damage(Properties + Crops)")

```
 
## Results

In this study, the top ten types of storms which cause the most fatalities and injuries,
and the top ten types of storms that brought most properties and crops damage were given.
Generally speaking, TORNADO, FLOOD, TSTM WIND etc. contribute the most in both situations.

